A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market

### 2013-08-30 reports/Draft.tex
worked on the Dakota County table and future research

We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, MN metropolitan area. Specifically, we estimate linear regressions at each house within our dataset using only information contained in geographically nearby houses sold within the last 12 months. We find strong evidence that the hedonic function in our study area differs over space and time. Local regressions using only information contained in the nearest 200 houses generate a substantially smaller Generalized Cross Validation score (0.266) compared to the same model assuming geographical stationarity in the regression coefficients (0.401).

Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not due to chance and that many hedonic impact estimates vary over space within our study area. When the location of our data was randomly assigned and our LWR model was re-estimated, in 100 consecutive simulations the smallest GCV score was  obtained when the data were analyzed at a global level rather than local. Additionally, re-estimating the LWR model using a local bandwidth of 200 nearest house sales when the location was randomly assigned yielded substantially smaller standard deviations for the majority of our regression coefficients. This larger variation within our true data suggests spatial non-stationarity in the regression coefficients. That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, we never came close to estimating our observed housing sales prices as well as we can with the local analysis on the actual data.

@@

>>>>

We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, Minnesota urban area. Specifically, we estimate semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' house sales (where local is defined both geographically and temporally). We find strong evidence that the hedonic function in our study area varies over space and time.

Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not due to chance and that many hedonic implicit prices vary over space within our study area. When the location of our data was randomly assigned and our LWR model was re-estimated across more than a dozen diferent bandwidths, in 100 consecutive simulations the smallest GCV score was obtained when the data were analyzed at a pooled/global level rather than local. That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, we never came close to estimating our observed housing sales prices as well as we can with the local analysis on the actual data. Additionally, re-estimating the LWR model using a local bandwidth of 200 nearest house sales but randomly assigned locations yielded substantially smaller standard deviations for the majority of our regression coefficients. Such differences suggest that the variation exhibited by most of our regression coefficients was not due to simple random chance, but instead is consistent with spatial non-stationarity.

@@

Finally, the results of this work suggest multiple areas of fruitful future research to better help policymakers weigh the costs and benefits of traffic noise. First, we suggest research be conducted in more housing markets, as the potential to apply the results of analysis in one set of geographical and economic circumstances may be limited. Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are alowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression. As mentioned previously, future work may also seek to re-estimate traffic noise models over time to better account for changes in traffic flows associated with macroeconomic conditions. Lastly, researchers may want to take advantage of the findings of \citet{Carruthers2010} and use the spatial variation in regression coefficients to help estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics.
